Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-21 cav2017/cav2017.tex
Swapped the 2 sections on different approaches
This makes it more consistent with rest of paper that refers to “first
approach” being the unwinding of the state space and “second approach”
being the acceleration

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalisation} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%Abstractly-Refined

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

The verification of a hybrid continuous/discrete time/space system over an unbounded time, requires the
non-deterministic simulation of an infinite set of states, which is undecidable. Our initial approach creates an
abstraction of this system by establishing bounds on the error between such a system and a discrete-time/space model.
This model is still however, quite complex, hard to verify, and many of the states involved are inconsequential to
the safety specification.
Our second model, rather than look at a direct bisimulation in discrete time, explores a much higher abstraction,
evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specifcation.
We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a
single iteration, in addition to a stability specification defined by Jury's criteria, and try to synthesise a controller that meets these specs.
A second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time is used to verify that the controller meets the full safety specification. If this step fails, we find a counterexmple iteration that causes the selected system to fail and create a new constraint to refine our abstraction.
The advantage of this model is that it starts with a very simple description regardless of the complexity of the overall dynamics, and only expands to more complex models when a solution cannot be found.

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalisation} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%Abstractly-Refined
In this section we outline the general architecture of the progam synthesizer used 
in both approaches. We then detail the 2 methods of solution generalisation that we compare.
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

The verification of a hybrid continuous/discrete time/space system over an unbounded time, requires the
non-deterministic simulation of an infinite set of states, which is undecidable. Our initial approach creates an
abstraction of this system by establishing bounds on the error between such a system and a discrete-time/space model.
This model is still however, quite complex, hard to verify, and many of the states involved are inconsequential to
the safety specification.
Our second approach, rather than look at a direct bisimulation in discrete time, explores a much higher abstraction,
evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specifcation.
We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a
single iteration, in addition to a stability specification defined by Jury's criteria, and try to synthesise a controller that meets these specs.
A second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time is used to verify that the controller meets the full safety specification. If this step fails, we find a counterexmple iteration that causes the selected system to fail and create a new constraint to refine our abstraction.
The advantage of this model is that it starts with a very simple description regardless of the complexity of the overall dynamics, and only expands to more complex models when a solution cannot be found.
